\documentclass[a4paper]{scrartcl}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{lastpage}
\usepackage{pgf}
\usepackage{wrapfig}
\usepackage{fancyvrb}
\usepackage[breaklinks=true]{hyperref}

% Listing header

\usepackage{listings}
\usepackage{xcolor}

\definecolor{lightgray}{gray}{0.95}

\lstdefinestyle{javastyle}{
    backgroundcolor=\color{lightgray},
    basicstyle=\ttfamily\small,
    numbers=left,
    numberstyle=\tiny,
    numbersep=8pt,
    frame=single,
    showstringspaces=false,
    breaklines=true,
    breakautoindent=true,
    breakindent=2em,
    keepspaces=true,
    columns=fullflexible,
    tabsize=4,
    language=Java,
    keywordstyle=\color{blue},
    commentstyle=\color{gray!70},
    stringstyle=\color{orange!90!black},
    literate=
      {Å}{{\AA}}1
      {å}{{\aa}}1
      {Ä}{{\"A}}1
      {ä}{{\"a}}1
      {Ö}{{\"O}}1
      {ö}{{\"o}}1
      {‑}{{-}}1
}

\lstdefinestyle{outputstyle}{
    basicstyle=\ttfamily\small,
    frame=single,
    breaklines=true,
    columns=fullflexible,
    keepspaces=true,
    showstringspaces=false,
    literate=
      {Å}{{\AA}}1
      {å}{{\aa}}1
      {Ä}{{\"A}}1
      {ä}{{\"a}}1
      {Ö}{{\"O}}1
      {ö}{{\"o}}1
      {‑}{{-}}1
}

% Create header and footer
\headheight 27pt
\pagestyle{fancyplain}
\lhead{\footnotesize{Object-Oriented Design, IV1350}}
\chead{\footnotesize{Seminar~3 Solution}}
\rhead{}
\lfoot{}
\cfoot{\thepage\ (\pageref{LastPage})}
\rfoot{}

% Create title page
\title{Seminar 4}
\subtitle{Object-Oriented Design, IV1350}
\author{Mo Wang mowang@ug.kth.se}
%\date{\today} Prints today's date
\date{2026-04-29}

\begin{document}

\maketitle
\noindent\textbf{Project Members:} \\ \hfill
% \tableofcontents %Generates the TOC
[Mo Wang, mowang@ug.kth.se]

\section*{Declaration:}

By submitting this assignment, it is hereby declared that all group members listed above have contributed to the solution. It is also declared that all project members fully understand all parts of the final solution and can explain it upon request.

It is furthermore declared that no part of the solution has been copied from any other source (except for resources presented in the Canvas page for the course IV1350), and that no part of the solution has been provided by someone not listed as a project member above.

\section{Introduction}
\label{sec:intro}

This report focus on exception handling and design pattern implementation of the \textit{Repair Electric Bike} system. The purpose of Seminar~4 is to extend the implementation design with exception for error handling as well as refactoring the code for design patterns. Additionally, the unit tests are also added to verify the code behavior for error handling as well. The implementation follows the principles and guidelines in Chapter~8 for error handling as well as design patterns in Chapter~9 of \textit{A First Course in Object-Oriented Development} \cite{coursebook}.

Exception handling are implemented as error handling, both business logic violations as well as internal failures. When the code in model fails, exceptions are thrown and propagated through function call layers until the view layer is reached. At that time, an error message is displayed, while the code stops. Instead of silent failures or propagating error messages using return values, error messages relies on exceptions which is reserved for handling errors.

In addition to error handling, design patterns are applied to improve the structure and maintainability of the system. Since these patterns address recurring design problems and contributes to higher encapsulation, cohesion and lower coupling, these are integrated into the system to make overall architecture more flexible and easier to extend.

Throughout the implementation of error handling and using design patterns, automated unit testing is also carried out in parallel. In each code development iteration, after developing the code for a specific purpose, the corresponding test cases are also added and updated in order to verify the code behavior. This ensures code quality throughout the development and makes incorrect behavior debuggable at an early stage. 

\subsection{Requirements of Seminar 4}

Seminar~4 consists of two main tasks: exception handling and design pattern implementation.

\subsubsection*{Task 1: Exception Handling}

The first task is to extend the Repair Electric Bike system with exception handling. The implementation must fulfill the following requirements:

\begin{itemize}
    \item Exceptions are used to handle alternative flow 5a, where a searched customer phone number does not exist in the customer registry. They are also used to simulate database failures by throwing an exception when searching for a specific hard-coded item identifier.
    
    \item Exceptions must follow best practices described in Chapter~8 of the course book:
    \begin{itemize}
        \item Appropriate choice between checked and unchecked exceptions.
        \item Exceptions are defined at the correct abstraction level.
        \item Exception classes are named after the error condition.
        \item Exceptions include relevant information about the error.
        \item Built-in functionality from \texttt{java.lang.Exception} is utilized.
        \item Javadoc comments are written for all exception classes.
        \item The system state must remain unchanged if an exception is thrown.
        \item Users are notified with meaningful error messages.
        \item Developers are notified through error logging to a file.
    \end{itemize}
    \item When an exception is caught in the view layer, an informative error message is displayed to the user.
    \item Severe errors are logged to a file for debugging and maintenance purposes.
    \item Unit tests are implemented to verify exception handling behavior.
\end{itemize}

\subsubsection*{Task 2: Design Patterns}

The second task is to apply design patterns to improve the system design.

\begin{itemize}
    \item The Observer pattern is implemented for active notification when a repair order is updated.
    \item A new view, \texttt{RepairOrderView}, prints updated repair orders to \texttt{System.out}.
    \item A second observer implementation, \texttt{RepairOrderLogger}, logs repair order updates to a file.
    \item Both observer implementations must implement the same observer interface and must not call the controller or other system components directly.
    \item For higher grade requirements, at least two additional Gang of Four (GoF) design patterns are implemented, excluding Observer and Template Method.
    \item The chosen patterns must be properly motivated and integrated into the system architecture.
\end{itemize}

\subsubsection*{Unit Testing}

\begin{itemize}
    \item Unit tests are implemented continously using the JUnit framework.
    \item Tests specifically verify exception handling and error scenarios.
    \item Tests ensure that exceptions are thrown under the correct conditions and that system state remains consistent.
\end{itemize}

\section{Method}

% \textbf{This chapter tells \textit{how} you solved the task.} Explain how you worked and what tools you used when solving the tasks. \textit{Do not explain your solution and do not present entire sub-results in detail. It's enough to explain which steps you performed and perhaps give a short example.} For example, some of the things to explain in the report for seminar one, is that you used a category list and noun identification to find class candidates for the domain model, and to tell which UML editor you used.
% Goal: Explain how you worked (not the solution itself)

% In the Method chapter of your report, explain how you worked and how you reasoned when implementing exception handling.

This chapter describes both the development process for implementing error handling using exceptions as well as applying design patterns in the code. Implementations are carried out while sticking to the code guidelines. Additionally, unit tests are written after each small implementation to ensure code correctness and quality.

\subsection{Exceptions as error handling}

For error handling implementation, exceptions has a reserved purpose for handling errors. Exception mechanism is dedicated for raising, propagating and handling errors, and is only used for handling errors, from business rule violations to internal program failures. Error messages are written inside exceptions to be as clear as possible. This means that error messages are not handled using return values, whereas the return values are reserved passing non-error business data. Additionally, successful execution and non-error business data doesn't either use exception mechanism. In this way, the border between non-error business logic and error handling mechanism is clearly separated and does not blend in with each other. 

\subsubsection{Checked and unchecked exceptions}

In terms of errors, there are two different error types for two exception types: business-rule violations and internal program failures. Business-rule violations are incorrect input from user and includes searching a non-existent customer or passing in a malformed telephone number and falls into the category of checked exceptions. These exceptions are declared in every propagated level API. On the other hand, internal progam failures are unrecoverable failures, such as database connection failures, which are handled by unchecked exceptions.

\subsubsection{Exception Design Principles}

Exception classes are designed to follow naming conventions. Each exception is named after error condition using descriptive names ending with \texttt{Exception}. Instead of creating many highly specific exception classes, a small number of well-defined exceptions were used, while detailed context was included in the exception message. Additionally, exceptions contains a descriptive message intended for developers, while avoiding exposure of internal implementation to user interface. This makes exception error messages useful and easier to debug the code.

To ensure the correct abstraction level, low-level exceptions from the integration layer, such as database connection issues, are not exposed directly to the view, but either handled or wrapped in higher-level exceptions before being propagated further. In my case, exceptions are wrapped when passing through a layer in the layered MVC-architecture. Also, unchecked exceptions are wrapped inside a checked exception \texttt{FailedOperationException} when passing from controller layer to view layer where only business-related checked exceptions exists.

Object should not either change its internal state when exception is thrown. Some operation does not inheritely alter the state, for instance the method \texttt{find} in \texttt{CustomerRegistry} class finds a customer using a telephone number. In this case, an exception \texttt{NotFoundCustomerException} can be thrown whenever the registry does not contain the corresponding telephone number. However, some classes ...

Objects are designed so that their internal state does not change when an exception is thrown. For operations that do not alter object state, such as searching for a customer in the \texttt{CustomerRegistry}, exceptions can be thrown directly without side effects. For state-changing operations, input parameters are validated before any state changes occur and operations that may fail are executed before modifying the object state. In situations where this is not feasible, temporary variables are used to ensure that updates are only applied after all checks have passed. These strategies guarantee that the system remains in a consistent state even when errors occur.

\subsubsection{Writing Javadoc for exceptions}

Additionally, methods that throws exceptions are documented using Javadoc \texttt{@throws}, which makes error condition explicit. The condition where the exception is thrown is documented clearly and serves as a guide to users of the method as well as keeping the developer to define the purpose of the exception. For instance, the method \texttt{find} in \texttt{CustomerRegistry} class finds a customer using a telephone number. If the telephone number does not correspond to any customer in the registry, a \texttt{NotFoundCustomerException} is thrown and propagated through the layer. The condition is stated in the method \texttt{find}, as well as the methods that propagate the exceptions.

\subsubsection{Notify user}

Error messages for users are handled in the view layer. When an exception reaches the view, it is caught and converted into a user-friendly error message, which is then displayed. These messages are designed to be clear and informative about business rule violations, without exposing internal system details. This avoids duplication and prevents lower-level components from directly interacting with the user interface.

\subsubsection{Notify developers}

Notifying error messages to developers is handled through a dedicated logging mechanism. When unchecked exceptions occur, they are logged to a file along with detailed diagnostic information, including stack traces, which allows developers to trace and debug errors effectively. Logging mechanism is implemented in a separate utility component to maintain separation of concerns. However, business-rule exceptions, such as malformed input, are not logged since they are expected execution behavior.

\subsubsection{Exception unit tests}

Exceptions are unit tested to ensure correct error handling behavior during different circumstances. The tests are written incrementally alongside development and implementation to verify both normal and error behavior where an exception is expected to be thrown.

The tests ensure that no exceptions are thrown during valid execution, and that appropriate exceptions are thrown under failure conditions. The execution messages are also verified to contain correct and useful information, and exceptions are properly propagated through layers.

Additionally, tests confirm that catch blocks handle exceptions as intended, including correct user notification and logging behavior. This ensures that the error-handling mechanism is reliable and behaves as expected in all relevant scenarios.

\subsection{Design Patterns}

Design patterns are also added and integrated into the program to improve structure, flexibility, and maintainability of the system. The patterns are used for identifying the recurring design problems when tight coupling between components and difficulties in extending functionalities are detected. In such case, a suitable GoF design pattern is found and used to refactor the existing code with tight coupling design in order to separate the concerns clearly. This results in higher code quality in terms of cohesion, encapsulation and low coupling.

The implementation process begins with analyzing the responsibility in the existing system and identifying the implementation parts that has tight coupling when functionality is extended. This also means the code parts where modification of multiple classes are needed during functionality extension. Patterns are therefore chosen to reduce the dependencies between the components.

There are multiple patterns being implemented in the code, each with the benefits.

The Observer pattern is implemented to handle updates of repair orders to \texttt{RepairOrderView}, which is an interactive display of the current repair order. Instead of letting the controller or view directly manage updates, a notification mechanism is introduced. This allows components interested in repair order updates to be notified automatically when changes occur. The pattern is applied by defining a common observer interface and letting multiple components implement it. These observers are then registered and notified through the model without creating direct dependencies between classes.

Polymorphism is also used when implementing design patterns. Interfaces are introduced to ensure that clients depend only on abstractions rather than concrete implementations This allows different implementations to be substituted without modifying existing code, improving flexibility and reducing coupling. For instance, switching between database handler and file handler for storage can be solved cleanly with polymorphism

When introducing additional design patterns, the focus is about separating responsibilities and avoiding hard-coded logic. Instead of embedding behavior directly into classes, behavior is encapsulated into separate components that can be configured or replaced. This approach makes the system easier to extend without modifying existing code.

Inheritance are used cautiously and only when a clear "is-a" relationship existed. It is used only in common functionalities, such as factoring out common parts of \texttt{ReceptionistController} and \texttt{TechnicianController} In most cases, composition are preferred over inheritance to maintain encapsulation and avoid tight coupling between classes.

Throughout the implementation, design decisions are evaluated based on their impact on cohesion, coupling, and encapsulation. Patterns are only applied when they provide a clear improvement to the design.

\section{Result}
\label{sec:result}

% \textbf{This chapter explains \textit{the result} of what you did.} \textbf{The report must show that you have done the work yourself and that you have understood what you have done}, both of these goals are met by explaining your solution here in the result chapter. Include links to your code in your Git repository (for seminars 3 and 4), and also include diagrams, see Figure \ref{fig:diag}, and other figures to illustrate your reasoning. All figures must be referenced in the text. Ask yourself if the solution is clearly explained, and if the reader will understand the application. What would you yourself want to know if you read about the application, is that included in the report? More specifiec instructions for the content can be found in each assignment.

\section{Result}

By extending the current implementation of the Repair Electric Bike System with exception handling, errors are now handled using a dedicated mechanism separated from the main business logic. Exceptions are used to for both business-rule violations and internal failures, and are propagated through the system layers until they are handled in the view.

Design patterns are also integrated to improve the code quality and program structure. For instance, the Observer pattern is implemented to notify an interactive \texttt{RepairOrderView} when repair orders are updated, which allows multiple views to react and update automatically without direct dependencies on the model or the controller.

In addition, logging functionality has been introduced to track internal program failures and making debugging easier, while user-friendly error messages are presented in the view. Business logic violations are only displayed in the view without writing into log, since the internal program still produces correct behavior.

Alongside the implementations, unit tests are written to verify both normal execution and error-handling behavior.

The complete source code for this seminar is available in the public Git repository at: \href{https://github.com/mo-mosverkstad/java-learning/tree/main/maven-projects/ElectricBikeRepair/}{\nolinkurl{https://github.com/mo-mosverkstad/java-learning/tree/main/maven-projects/ElectricBikeRepair/}} \cite{sourcecode}.

\subsection{Error handling using exceptions}

In terms of error handling using exceptions, custom exception classes are extended from \texttt{Exception} base class to cover different groups of error condition. Business-rule violations are represented using checked exceptions, while internal failures are represented using unchecked exceptions.

When an error occurs in the model or integration layer, an appropriate exception is thrown and propagated through the system layers, which are shown in listings, related to the specific exception. Business-related exceptions are allowed to propagate to the view, where they are handled and presented as user-friendly error messages. Internal exceptions, such as simulated database failures, are caught in the controller layer and wrapped in a higher-level exception before being propagated further.

\subsubsection{InvalidTelephoneNumberException}

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Thrown when a telephone number has an invalid format and cannot be parsed.
 */
public class InvalidTelephoneNumberException extends Exception {
    /**
     * Creates an exception indicating the given telephone number is invalid.
     *
     * @param telephoneNumber the telephone number that could not be parsed
     */
    public InvalidTelephoneNumberException(String telephoneNumber){
        super(String.format("The phone number %s is not a valid phone number", telephoneNumber));
    }
}
\end{lstlisting}


se.ebikerepair.util.TelephoneNumber constructor
\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Parses a telephone number string into country code, area code, and subscriber number.
 *
 * @param telephoneNumber the telephone number in any supported Swedish format
 * @throws InvalidTelephoneNumberException if the telephone number is null, empty, or has an invalid format
 */
public TelephoneNumber(String telephoneNumber) throws InvalidTelephoneNumberException {
    if (telephoneNumber.trim().isEmpty()) {
        throw new InvalidTelephoneNumberException("<empty>");
    }

    String digits = telephoneNumber.replaceAll("[\\s\\-\\(\\)]", "");

    if (!digits.matches("\\+?[0-9]+")) {
        throw new InvalidTelephoneNumberException(telephoneNumber);
    }

    // ... normalization logic ...

    if (normalized.length() < 7) {
        throw new InvalidTelephoneNumberException(telephoneNumber);
    }

    // ... extraction logic ...

    if (remaining.isEmpty() || (remaining.length() < 8 || remaining.length() > 9)) {
        throw new InvalidTelephoneNumberException(telephoneNumber);
    }

    // ...

    if (sn.isEmpty()) {
        throw new InvalidTelephoneNumberException(telephoneNumber);
    }
}
\end{lstlisting}

se.ebikerepair.controller.Controller, findRepairOrderIds

\begin{lstlisting}[style=javastyle, caption={...}]
private List<String> findRepairOrderIds(String telephoneNumber) throws InvalidTelephoneNumberException{
    String phoneNumberE164 = new TelephoneNumber(telephoneNumber).toE164();
    // process phoneNumberE164 ...
}
\end{lstlisting}

se.ebikerepair.controller.Controller, findRepairOrder

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Finds the most recent repair order for the given telephone number.
 *
 * @param telephoneNumber the customer's telephone number (any Swedish format)
 * @return the most recent repair order as a DTO
 * @throws InvalidTelephoneNumberException if the phone number format is invalid
 * @throws NoExistedRepairOrderException if no repair orders exist for the customer or the order cannot be found
 */
public RepairOrderDTO findRepairOrder(String telephoneNumber) throws InvalidTelephoneNumberException, NoExistedRepairOrderException{
    List<String> repairOrderIds = findRepairOrderIds(telephoneNumber);
    // further process
}
\end{lstlisting}

`se.ebikerepair.controller.ReceptionistController` — searchCustomer, createRepairOrder

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Searches for a customer by telephone number.
 *
 * @param telephoneNumber the customer's telephone number (any Swedish format)
 * @return the found customer DTO
 * @throws NotFoundCustomerException if the phone number does not correspond to a customer
 * @throws InvalidTelephoneNumberException if the telephone number is empty or invalid
 * @throws FailedOperationException if an underlying infrastructure error occurs, such as a database or file system failure
 */
public CustomerDTO searchCustomer(String telephoneNumber) throws NotFoundCustomerException, InvalidTelephoneNumberException, FailedOperationException{
    try {
        String phoneNumberE164 = new TelephoneNumber(telephoneNumber).toE164();
        return customerRegistry.find(phoneNumberE164);
    } catch (ResourceNotFoundException | InvalidResourceURIException | CannotReadFileException | CannotWriteFileException | NoDatabaseException exception){
        LogHandler.getLogger().logException(exception);
        throw new FailedOperationException("Fail to search customer", exception);
    }
}

/**
 * Creates a new repair order for the customer identified by telephone number.
 *
 * @param telephoneNumber the customer's telephone number (any Swedish format)
 * @param problemDTO the problem description with the broken bike
 * @return the generated repair order ID
 * @throws NotFoundCustomerException if the customer is not found
 * @throws InvalidTelephoneNumberException if the telephone number is empty or invalid
 * @throws FailedOperationException if an underlying infrastructure error occurs, such as a database or file system failure
 */
public String createRepairOrder(String telephoneNumber, ProblemDTO problemDTO) throws NotFoundCustomerException, InvalidTelephoneNumberException, FailedOperationException{
    try {
        CustomerDTO foundCustomer = searchCustomer(telephoneNumber);
        RepairOrder repairOrder = new RepairOrder(foundCustomer);
        repairOrder.addRepairOrderObservers(repairOrderObservers);
        repairOrder.updateProblem(problemDTO);
        repairOrderRegistry.save(repairOrder);
        return repairOrder.getId();
    } catch (ResourceNotFoundException | InvalidResourceURIException | CannotReadFileException | CannotWriteFileException | NoDatabaseException exception){
        LogHandler.getLogger().logException(exception);
        throw new FailedOperationException("Fail to create repair order", exception);
    }
    
}
\end{lstlisting}

View proceedactions

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Runs the full repair workflow: reception preparation, technician diagnostics, and reception confirmation.
 *
 * @param telephoneNumber the customer's telephone number
 * @param bikeSerialNumber the serial number of the broken bike
 */
public void proceedActions(String telephoneNumber, String bikeSerialNumber) {
    try{
        proceedReceptionPreparationActions(telephoneNumber, bikeSerialNumber);
        proceedTechnicianDiagnosticActions(telephoneNumber);
        proceedReceptionConfirmationActions(telephoneNumber);
    } catch (NotFoundCustomerException | InvalidTelephoneNumberException | FailedOperationException | NoExistedRepairOrderException | IllegalArgumentException e) {
        System.out.println(ERROR_PREFIX + e.getMessage());
        LogHandler.getLogger().logException(e);
    }
}
\end{lstlisting}

\subsubsection{ResourceNotFoundException (unchecked)}

`se.ebikerepair.data.ResourceNotFoundException`

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Thrown when a classpath resource file cannot be found.
 */
public class ResourceNotFoundException extends RuntimeException{
    /**
     * Creates an exception indicating the resource was not found.
     *
     * @param resourceName the name of the resource that was not found
     */
    public ResourceNotFoundException(String resourceName) {
        super(String.format("%s not found in resources", resourceName));
    }
}
\end{lstlisting}

`se.ebikerepair.data.JsonFileHandler` — initDataHandler -> `se.ebikerepair.model.DiagnosticReport` — loadDiagnosticTasks -> `se.ebikerepair.integration.CustomerRegistry` — initRegistry

`se.ebikerepair.controller.ReceptionistController` — searchCustomer, createRepairOrder

\begin{lstlisting}[style=javastyle, caption={...}]
/**
 * Searches for a customer by telephone number.
 *
 * @param telephoneNumber the customer's telephone number (any Swedish format)
 * @return the found customer DTO
 * @throws NotFoundCustomerException if the phone number does not correspond to a customer
 * @throws InvalidTelephoneNumberException if the telephone number is empty or invalid
 * @throws FailedOperationException if an underlying infrastructure error occurs, such as a database or file system failure
 */
public CustomerDTO searchCustomer(String telephoneNumber) throws NotFoundCustomerException, InvalidTelephoneNumberException, FailedOperationException{
    try {
        String phoneNumberE164 = new TelephoneNumber(telephoneNumber).toE164();
        return customerRegistry.find(phoneNumberE164);
    } catch (ResourceNotFoundException | InvalidResourceURIException | CannotReadFileException | CannotWriteFileException | NoDatabaseException exception){
        LogHandler.getLogger().logException(exception);
        throw new FailedOperationException("Fail to search customer", exception);
    }
}

/**
 * Creates a new repair order for the customer identified by telephone number.
 *
 * @param telephoneNumber the customer's telephone number (any Swedish format)
 * @param problemDTO the problem description with the broken bike
 * @return the generated repair order ID
 * @throws NotFoundCustomerException if the customer is not found
 * @throws InvalidTelephoneNumberException if the telephone number is empty or invalid
 * @throws FailedOperationException if an underlying infrastructure error occurs, such as a database or file system failure
 */
public String createRepairOrder(String telephoneNumber, ProblemDTO problemDTO) throws NotFoundCustomerException, InvalidTelephoneNumberException, FailedOperationException{
    try {
        CustomerDTO foundCustomer = searchCustomer(telephoneNumber);
        RepairOrder repairOrder = new RepairOrder(foundCustomer);
        repairOrder.addRepairOrderObservers(repairOrderObservers);
        repairOrder.updateProblem(problemDTO);
        repairOrderRegistry.save(repairOrder);
        return repairOrder.getId();
    } catch (ResourceNotFoundException | InvalidResourceURIException | CannotReadFileException | CannotWriteFileException | NoDatabaseException exception){
        LogHandler.getLogger().logException(exception);
        throw new FailedOperationException("Fail to create repair order", exception);
    }
    
}
\end{lstlisting}

\subsection{Error handling unit tests}


\begin{lstlisting}[style=javastyle, caption={...}]
public class TelephoneNumberTest {
    @Test
    void testInternationalPrefix() {
        assertDoesNotThrow(() -> {
            TelephoneNumber number = new TelephoneNumber("0046701234567");
            assertEquals("+46701234567", number.toE164());
        });
    }

    @Test
    void testWrongPrefix() {
        assertThrows(InvalidTelephoneNumberException.class, () -> {
            TelephoneNumber number = new TelephoneNumber("0001234567");
            number.toE164();
        });
    }
}
\end{lstlisting}

\begin{lstlisting}[style=javastyle, caption={...}]

\end{lstlisting}

\begin{lstlisting}[style=javastyle, caption={...}]

\end{lstlisting}

\begin{lstlisting}[style=javastyle, caption={...}]

\end{lstlisting}

\subsection{Design pattern designs}
...

\section{Discussion}

\begin{thebibliography}{9}

\bibitem{coursebook}
Leif Lindbäck,
\textit{A First Course in Object-Oriented Development --- A Hands-On Approach},
Course material for IV1350,
KTH Royal Institute of Technology,
January 14, 2026.

\bibitem{sourcecode}
Mo Wang,
``ElectricBikeRepair --- Source code for Seminar~3,''
2026.
[Online]. Available: \url{https://github.com/mo-mosverkstad/java-learning/tree/main/maven-projects/ElectricBikeRepair/}

\end{thebibliography}

\end{document}
